FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance

### 2017-06-15 Aplas17/sections/Formalization.tex
Notes on uparrow.
Some text

Figure~\ref{fig:syntax} shows the syntax of \MIM{}. The multiple
inheritance feature of \MIM{} as a basis Java 8 interfaces, which support
method implementations via default methods. This feature is quite
closely related to \emph{traits}\cite{scharli03traits}.  To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we present the
calculus in a straightforward way, hence we only focus on a small
subset of the interface model. For example, all the methods declared
in an interface are default methods, that is to say, they always
provide default implementations.  From this point we can view that we
are actually modelling a class model that supports multiple
inheritance. Then it is straightforward to do object creation like
$\new I$. Fields and primitive types are not modelled as well.

>>>>

Figure~\ref{fig:syntax} shows the syntax of \MIM{}. The multiple
inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
method implementations via default methods. This feature is quite
closely related to \emph{traits}~\cite{scharli03traits}.  To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we present the
calculus in a straightforward way, hence we only focus on a small
subset of the interface model. For example, all the methods declared
in an interface are default methods, that is to say, they always
provide default implementations.  From this point we can view that we
are actually modelling a class model that supports multiple
inheritance. Then it is straightforward to do object creation like
$\new I$. Fields and primitive types are not modelled as well.
